SpatialEpi

### 2016-08-19 README.Rmd
Starting clean-up.

---
title: "SpatialEpi"
output: github_document
---

[![Travis-CI Build Status](https://travis-ci.org/rudeboybert/SpatialEpi.svg?branch=master)](https://travis-ci.org/rudeboybert/SpatialEpi)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/SpatialEpi)](http://cran.r-project.org/package=SpatialEpi)

>>>>

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# SpatialEpi

[![Travis-CI Build Status](https://travis-ci.org/rudeboybert/SpatialEpi.svg?branch=master)](https://travis-ci.org/rudeboybert/SpatialEpi)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/SpatialEpi)](http://cran.r-project.org/package=SpatialEpi)
[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/SpatialEpi)](http://www.r-pkg.org/pkg/SpatialEpi)
